Toxic Code Snippets on Stack Overflow

### 2018-05-24 cloverflow-tse/cover_letter/cover_letter.tex
After the Grammarly check.

%\begin{abstract}
This paper is a journal-first submission to Transactions on Software
Engineering. This is a re-submission of the previous submission
no.~TSE-2017-11-0335 and we would like to thank the anonymous reviewers for
taking their time to carefully read our paper. With their useful and
constructive reviews, we substantially improved the work by adding five major
improvements as listed below to our previous submission and minor improvements
as discussed later in this letter.

\textbf{1.~A Stack Overflow Visitor survey}~To understand the effects of toxic
code snippets on Stack Overflow to information seekers who look for coding
solutions on Stack Overflow, we performed another survey of 87 Stack Overflow
visitors. The survey shows that the visitors experienced several problems from
reusing Stack Overflow code snippets including outdated code. They are 85\% of
them that are not aware of CC BY-SA 3.0 license enforced by Stack Overflow and
66\% never check for license conflicts when reusing code snippets.

@@

\textbf{4.~An extended analysis of outdated code clones:}~We performed an
extended analysis on the 100 outdated code snippets. For example, we analysed
age of the clones; studied effects of comments, newer answers, higher-voted
answers on the outdated answers; and summarised the six intents that made the
clones outdated. We found that, on average, the code is cloned to Stack Overflow
2 years after it appears in Qualitas projects, and comments/newer or
higher-voted answers did not strongly affect the outdated answers (99\% are
still marked as accepted). Lastly, we discovered that the code are outdated
because of code enhancement (65\%), followed by code deprecation (15\%), but
fixing (10\%), code refactoring (6\%), changing coding style (3\%), and data
format change (2\%).

@@

We also tried our best to address all the comments from the reviewers. Every
comment led to an improvement on this submission and we discuss them in order as
shown in the next sections.

@@

We would like to thank the reviewer for the comments.~We agree with the suggestion and we made the following changes to the paper:

\begin{enumerate}
	\item We understand the concern of finding real evidence to support the claim that code snippets on Stack Overflow do appear in open- or closed-source software projects. Hence, we have performed a study of code clone detection between our 100 reported outdated code snippets on Stack Overflow and 131,703 GitHub projects. We selected SourcererCC with 80\% similarity for this experiment because it could scale to a large-scale data set, while Simian could not. We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them. As shown in Table~\ref{tab:outdated_github} below, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub. For other projects besides the Qualitas projects, there were 47 cloned snippets that were exactly the same as the outdated code snippet and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).

@@

	Among the exact-copy of 47 outdated cloned snippets, there were only two cloned
snippets that gave attributions to Stack Overflow. However, the attributions
pointed to different posts than the ones we found, but containing the same code
in the answers. The other 32 cloned snippets were very likely to be a
file-level clone from its respective original project (e.g. JFreeChart, JUnit,
Log4J, Hadoop) based on their license header and the Javadoc comments. Lastly,
the remaining 13 cloned snippets did not have any hints or evidence of copying.
Twelve of them were toxic because they were the old versions that still
contained bugs.

@@

	\item The same study has been done for another type of toxic code snippets on
Stack Overflow, license-incompatible code snippets. We detected clones between
the 214 code snippets without their original license (86 QS, 78 EX and 50 UD) 
and 130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
In contrast to the outdated clones, we discovered many more clones of 7,207
candidate pairs. 
There were 95 pairs from 10
Qualitas projects hosted on GitHub and 7,112 pairs from 2,427 other projects.
Then, we used the Ninka tool to automatically identify
software licenses from the reported cloned snippets. Shown in
Table \ref{tab:license_github} below, the clones were found in highly-starred
projects (29,465 to 10 stars) to 1-star projects. We found 12 code snippets
with attributions to Stack Overflow questions/answers and 6 of them were the
answers we found as clones from Qualitas or external sources. Five code
snippets did not have a license while the originals had the Apache-2, GPLv2, or EPLv1
license. One snippets had the AGPLv3 license while the original had the Apache-2
license. Only 995 code snippets in GitHub projects have the same license
as the originals in Qualitas.

@@

	\item With the finding above, we show that clones of toxic Stack Overflow 
code fragments do occur in several open source software projects on GitHub.
However, we could not establish strong evidence that the toxic code snippets
were originated from Stack Overflow due to lack of supporting information.
Hence, we softened our claim by changing the statement ``\textit{It is probably
	more important than studying the effects of reusing Stack Overflow code
	snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the
	effects of reusing Stack Overflow code snippets ...}''. We also updated the
Overall Discussion section to reflect the findings that (1) there is only a
small number of toxic code snippets from outdated code that are found in GitHub
projects, (2) there is a large number of toxic code snippets caused by missing
license that are found in GitHub projects. %Moreover, the direction of copying
% is also unclear. The clones could come from Stack Overflow, the original
% project repositories, or other places.
\end{enumerate}

@@

We partially address this comment in the previous answer by performing an
empirical study of code cloning between toxic Stack Overflow code snippets and
GitHub projects. Furthermore, we also improved the paper on the aspect of the
awareness of information-seekers to toxic code snippets on Stack Overflow by
including the results from another survey of Stack Overflow visitors
(i.e.~information seekers). This survey of the Stack Overflow visitors was
performed during the same time as the Stack Overflow answerers (25 July 2017 to
25 September 2017) and the full results are reported in our technical
report~\citep{Ragkhitwetsagul_RN2017}. We did not include the results in the
previous version of the paper due to a smaller sample size compared to the
answerers survey. However, we did find some interesting results so we have
included them into this version and discussed the key findings in~RQ1. The brief
summary of the visitor survey is as follows.

@@

The visitors survey confirms the findings from the previous studies that Stack
Overflow code snippets can be problematic~\citep{Zhang2018,Acar2016,An2017}. Sixty-six
percent of the visitors experienced a problem from reusing Stack Overflow code
snippets ranging from incorrect solutions, outdated solutions, mismatched
solutions, to buggy code. Although they are aware of the problems, half of them
(56\%) never report back to the Stack Overflow discussions. On the other hand,
the visitors rarely give attributions to Stack Overflow when they reuse code
snippets from the website, similar to the findings reported
by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
license, and more than half of them never check for license compatibility when
reusing Stack Overflow code snippets. 
Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
check if the code snippet originated from a different source (e.g.~an open source project) 
and if they had an incompatible license to their projects.
Moreover, we also found that 9\% of the participants
encountered legal issues by copying code from Stack Overflow. To the best of our
knowledge, a study of legal problems from reusing Stack Overflow code snippets
has never been done before and will be our future work.

@@

\begin{enumerate} \item We added a discussion of toxicity of outdated and
	license-incompatible clones on Stack Overflow. Although we found some harmful
	outdated clones, we could not find evidence that they are widely reused in open
	source projects on GitHub. Therefore, the damage is not high since there are only
	a few outdated code snippets that are harmful for reuse. On the other hand, the
	problem of license incompatibility caused by missing original licenses in Stack
	Overflow code snippets can cause more damage than outdated code. Different legal
	system and different interpretation of fair-use concept and de minimis (i.e.~the
	minimal lines of code allowed to be copied without violating copyright) in each
	country can make a reuse of these code snippets legally problematic.

@@

You are right. We mainly study online code clones and established their
existence. However, we used the term ``toxic code snippets'' in order to
emphasise the possible ramifications from online code cloning. Moreover, the
term code cloning is not well known outside the code cloning community. Code
clones are called differently in each research community or in practice, such as
duplicated code, copy-and-paste code, code reuse, software similarity or
software redundancy. So, we decided not to use the term in the title.

@@

``Although this activity of online code cloning is well-known, there are only a
few empirical studies on the topic~\citep{An2017,Abdalkareem2017,Baltes2017},
especially on finding the origins of the clones. We tackle this challenge of
establishing existence of online code clones and investigate how they occur in
this study.'' %Considering your suggestion and another suggestion by Reviewer 2
% that the definition of ``toxic code snippets'' is vague, we also tightened the
% definition of toxic code snippets to be more precise.

@@

That is a fair point and we would like to analyse the statistics as you
suggested. To answer your question (a), the number of views is for the whole
Stack Overflow post but we use it as a proxy of the number of views the accepted
answer receives because the question and the answer of the two motivation
examples have a short gap of posting time (within the same day and four days
after). For (b), unfortunately, for our experiment we extracted only the code
snippets from the Stack Overflow dumps but not other information. They are the
only available data of the January 2016 snapshot we currently have. We checked
and found that the latest available Stack Overflow dump already contains
different data than the one we used in our study since it is more than 2
years newer, and will result in incorrect statistics and inconsistent results.
For (c), that is a really interesting idea. However, it is out of the scope of
this study and would involve an extensive analysis of the data so we may
investigate it in the future work.

Nevertheless, we have added a footnote to the text in the Introduction to
clarify point (a).

@@

Thank you for the detailed checking of the Stack Overflow post. Interestingly,
this is surprising to us as well. The comment in the post 22262310 by Joseph K
on 31 October 2017 that highlights the missing line in HADOOP \texttt{compare}
method is actually from a student in our class. His name is Joseph Kalash and he
is a master student in Machine Learning MsC program at UCL Computer Science
department\footnote{Joseph's CV can be found here: \url{https://jkala.sh/cv}}.
We assigned a preprint of this paper to students in the COMPGS11 -- Research
Seminar in Software Engineering course and had a discussion about the paper on
Thu 2 November 2017. Joseph, who was an active Stack Overflow member, was one of
the students in the class and he actively participated in the discussion. It
seems that he had seen the Hadoop's toxic code snippet in the paper and decided
to post a comment to warn other users.

Nevertheless, since this is a very interesting suggestion, we also performed an
investigation of the 100 answers of our reported outdated code snippets on Stack
Overflow on 6 May 2018 to see if there is any comment to mitigate or point out
the toxicity of the code snippet. We include the result of this investigation in
RQ4. We found that out of 100 answers containing outdated code snippets,
there were 6 answers that had a comment saying the code in the answer is
outdated or contains issues (including Joseph's comment). Thus, there are about
6\% of outdated answers that were notified by the Stack Overflow users based on
our analysed data. None of the 6 answers change their outdated code, but the
comments themselves may help to warn other Stack Overflow users. We added this
discussion to RQ4.

@@

\begin{enumerate} \item For the Stack Overflow data set, the value represents
	the median size of Stack Overflow code snippets. For the Qualitas data set, the
	value represents the median of number of lines of code in each project. Since
	they are confusing as you pointed out, we decided to remove them from the table
	and only discuss the numbers in the text. \item This is actually a great
	insight! We expanded the idea further and came up with a suggestion for an
	automated technique to facilitate human investigator on finding provenance and
	included it in a section called Automated cloning direction detection in the
	Overall Discussion. \item Thanks. This has been fixed. \end{enumerate}

@@

\rcomment{ \textbf{The definition of toxic code snippets:} I understand that the
	authors are trying to put a new spin or name to the phenomena they study, but
	the definition the authors provide is, in my opinion, not sufficient. For
	example, their definition is ``toxic code snippets mean code snippets that are
	harmful for reuse and, \textbf{in several cases}, are caused by online...''. A
	definition should be clear - saying in several cases - means that in several
	other cases (1- your several cases) it is not harmful. So, I ask the authors to
	refine and clarify this definition, because as it stands now, this definition is
	confusing (at best). Given that your entire paper is about toxic code snippets,
	you can appreciate why this is important. }

We appreciate the comments. We have refined our definition of toxic code
snippets in the paper by adapting Israel Gat's definition~\citep{toxiccode}
which links toxic code to technical debt, i.e.~``a metaphor reflecting technical
compromises that can yield short-term benefit but may hurt the long-term health
of a software system''~\citep{Li2015}. The new definition of toxic doe snippets
are as follows.

``Toxic code snippets mean code snippets that, after incorporating into
software, the cost of paying back the technical debt exceeds the value it
generates in the long run.'' Stack Overflow code snippets cloned from open
source software or online sources can become toxic when they are (1)~outdated,
(2)~violating their original software license, (3) exhibiting code smells, or
(4) having security vulnerabilities. We chose to study toxic code snippets
caused by outdated code and license-violating code snippets in this study since
these two problems are still under explored compared to code
smells~\citep{Tufano2015} or vulnerabilities~\citep{Acar2016,Fischer2017}.
Outdated code snippets can be harmful since they are not up-to-date with their
originals and may contain defects. Code snippets from open source projects
usually fall under a specific software license, e.g.\ GNU General Public License
(GPL). If they are cloned to Stack Overflow answers without the license, and
then flow to other projects with conflicting licenses, legal issues may occur.

@@

Regarding RQ5 (the Stack Overflow answerer survey), that is a good point. Since
RQ5 actually supports the motivation of our experiment by showing that code
copying from software projects to Stack Overflow actually occurs and showing
that some of the answerers are not aware of outdated code and software license
incompatibility. We moved them to RQ1 instead and reorganised the paper to
discuss the survey results as an incentive for our experiment of online code
clone detection and toxic code snippet identification. The findings in RQ2--5
will confirm the survey results by showing that the issues actually occur on
Stack Overflow.

@@

Stack Overflow allows its users to edit their own posts,
i.e.~questions/answers\footnote{https://meta.stackoverflow.com/questions/315915/i-am-not-allowed-to-edit-my-own-question}, or other user's posts\footnote{https://stackoverflow.com/help/privileges/edit}. Thus, if the code snippet in an answer is outdated and has an issue, the answerer or other high-reputation users can update the answer to be up-to-date or to warn other users that the code is already outdated and may contain problems. We found some discussions regarding this concern on Metaexchange as well so the Stack Overflow community is also considering this option\footnote{Discussion about outdated answer: https://meta.stackexchange.com/questions/131495/how-to-handle-outdated-answers and https://meta.stackexchange.com/questions/180864/editing-outdated-source-code-in-an-answer}. We included this discussion in the paper.

Based on your suggestion of looking at other newer or higher-voted answers, we
performed an investigation of all the answers in 100 posts containing outdated
code snippets as accepted answers. We found that there were 34 posts which
contains newer answers. Regarding the number of votes, there were 5 posts which
contained other answers with a higher number of votes than the outdated answer.
Ninety-nine out of the one hundred outdated code snippets were still marked as accepted
answers. This discussion of the findings is added to RQ4.

@@

Good point. Although we grouped the code modifications that make Stack Overflow
snippets outdated into 6 categories as shown in Table 9, we did not investigate
the motivation of the changes such as code refactoring or variable renaming. We
have performed the check as you suggested by checking the commit message of each
change that make the code outdated. The findings are discussed below and are
included in RQ4.

We looked through the commit history of 100 outdated code snippets and
summarised the reasons of code updates. We carefully read the commit messages
and/or used the bug IDs in the commit messages to obtain more information from
the bug report systems. We summarised the reasons of code changes into 6 groups
as shown in the table below.

\begin{table}[H]
	\centering
	\begin{tabular}{llr}
		\toprule
		Intent & Detail & Amount \\
		\midrule
		Enhancement & Add or update existing features & 64 \\
		Deprecation & Delete dead/deprecated code & 15 \\
		Bug & Fix bugs & 10 \\
		Refactoring & Refactor code for better design & 6 \\
		Coding style & Update to a new style guideline & 3 \\
		Data change & Changes in data format & 2 \\
		\bottomrule
	\end{tabular}
	\label{tab:intent_outdated}
	\caption{Intents of code changes in 100 outdated code snippets}
\end{table}

The majority (64) of the changes are due to code enhancement, such as adding a
new features or improving existing code to support a newer version of the
language or APIs. Fifteen changes are for removal of dead or deprecated code
such as the SQL connection code example in Hibernate. Ten changes are made to
fix bugs in the software (e.g.~array reference, race condition, wrong field
access, \texttt{NullPointerException}). There are 6 changes for code
refactoring, 3 changes for updating coding styles using an automated tool or
manually, and 2 changes that are caused by the change of data format.

@@

That is a fair point. The reason we chose the clone size of at least 10 lines is
because it is considered a standard setting for clone detection in large-scale
data sets to avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or
getter and setter methods) in the analysis or the manual investigation
phase~\citep{Sajnani2016}.

@@

To measure the impact of this minimum clone size threshold on the clone results,
we performed an investigation of three different threshold values: six, ten, and
fifteen lines. We started our investigation by using a threshold value of six
lines, a well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
clone candidate pairs. We randomly sampled 382 pairs from the two sets for
manual check. This sample number was a statistical significant sample with a
95\% confidence level and $\pm 5\%$ confidence interval. The first author
investigated the sampled clone pairs and classified them into three groups:
non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
setter methods), and non-trivial clones. The manual check found 26 non-clone
pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we
increased the threshold to ten lines, another well-established minimum clone
size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs
from Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and
manually checked the same amount of 382 pairs and found 27 non-clone pairs, 253
trivial clone pairs and 102 non-trivial clone pairs. Then, we increased the
threshold further to fifteen lines and retrieved 196 clone pairs from Simian and
1,230 clone pairs from SourcererCC. The manual check of the 382 randomly sampled
pairs reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial
clone pairs.

@@

We are grateful for the insightful comment. We selected the 2013 snapshot of
Qualitas data since it is the latest and the most complete snapshot (i.e.~having
the highest number of Java projects) provided by the data set author.

>>>>

%\begin{abstract}
This paper is a journal-first submission to Transactions on Software
Engineering. This is a re-submission of the previous submission
no.~TSE-2017-11-0335 and we would like to thank the anonymous reviewers for
taking their time to read our paper carefully. With their useful and
constructive reviews, we substantially improved the work by adding five major
improvements as listed below to our previous submission and minor improvements
as discussed later in this letter.

\textbf{1.~A Stack Overflow Visitor survey}~To understand the effects of toxic
code snippets to information seekers who look for coding
solutions on Stack Overflow, we performed another survey of 87 Stack Overflow
visitors. The survey shows that the visitors experienced several problems from
reusing Stack Overflow code snippets including outdated code. They are 85\% of
them that are not aware of CC BY-SA 3.0 license enforced by Stack Overflow and
66\% never check for license conflicts when reusing code snippets.

@@

\textbf{4.~An extended analysis of outdated code clones:}~We performed an
extended analysis of the 100 outdated code snippets. For example, we analysed
the age of the clones; studied effects of comments, newer answers, higher-voted
answers on the outdated answers; and summarised six intents that made the
clones outdated. We found that, on average, the outdated code snippets were cloned to Stack Overflow
2 years after it appeared in Qualitas projects, and comments/newer or
higher-voted answers did not strongly affect the outdated answers (99\% are
still marked as accepted). Lastly, we discovered that the code snippets are outdated
because of code enhancement (65\%), followed by code deprecation (15\%), but
fixing (10\%), code refactoring (6\%), changing coding style (3\%), and data
format change (2\%).

@@

\clearpage
We also tried our best to address all the comments from the reviewers. Every
comment led to an improvement on this submission, and we discuss them in order as
shown in the next sections.

@@

We would like to thank the reviewer for the comments.~We agree with the
suggestion, and we made the following changes to the paper:

\begin{enumerate} \item We understand the concern of finding real evidence to
	support the claim that code snippets on Stack Overflow do appear in open- or
	closed-source software projects. Hence, we have performed a study of code clone
	detection between our 100 reported outdated code snippets on Stack Overflow and
	131,703 GitHub projects. We selected SourcererCC with 80\% similarity for this
	experiment because it could scale to a large-scale data set, while Simian could
	not. We found 102 cloned candidates appearing in 68 GitHub projects and manually
	investigated all of them. As shown in Table~\ref{tab:outdated_github} below, out
	of the 102 cloned snippets, 13 cloned snippets matched with
	themselves because some of the Qualitas projects also appear on GitHub. For
	other projects besides the Qualitas projects, 47 cloned snippets
	were exactly the same as the outdated code snippet and 42 cloned snippets that
	were not the same (e.g.,~they contained additional code modifications
	made by the projects' developers, or they were copied from another source with a
	slightly different code).

@@

Among the exact-copy of 47 outdated cloned snippets, there were only two cloned
snippets that gave attributions to Stack Overflow. However, the attributions
pointed to different posts than the ones we found but containing the same code
in the answers. The other 32 cloned snippets were very likely to be a
file-level clone from its respective original project (e.g.,~JFreeChart, JUnit,
Log4J, Hadoop) based on their license header and the Javadoc comments. Lastly,
the remaining 13 cloned snippets did not have any hints or evidence of copying.
Twelve of them were toxic because they were the old versions that still
contained bugs.

@@

	\item The same study has been done for another type of toxic code snippets on
Stack Overflow, license-incompatible code snippets. We detected clones between
the 214 code snippets without their original license (86 QS, 78 EX, and 50 UD) 
and 130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
In contrast to the outdated clones, we discovered many more clones of 7,207
candidate pairs. 
There were 95 pairs from 10
Qualitas projects hosted on GitHub and 7,112 pairs from 2,427 other projects.
Then, we used the Ninka tool to identify
software licenses from the reported cloned snippets automatically. Shown in
Table \ref{tab:license_github} below, the clones were found in highly-starred
projects (29,465 to 10 stars) to 1-star projects. We found 12 code snippets
with attributions to Stack Overflow questions/answers and 6 of them were the
answers we found as clones from Qualitas or external sources. Five code
snippets did not have a license while the originals had the Apache-2, GPLv2, or EPLv1
license. One snippet had the AGPLv3 license while the original had the Apache-2
license. Only 995 code snippets in GitHub projects have the same license
as the originals in Qualitas.

@@

	\item With the finding above, we show that clones of toxic Stack Overflow 
code fragments do occur in several open source software projects on GitHub.
However, we could not establish strong evidence that the toxic code snippets
were originated from Stack Overflow due to lack of supporting information.
Hence, we softened our claim by changing the statement ``\textit{It is probably
	more important than studying the effects of reusing Stack Overflow code
	snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the
	effects of reusing Stack Overflow code snippets ...}''. We also updated the
Overall Discussion section to reflect the findings that (1) there is only a
small number of toxic code snippets from outdated code that are found in GitHub
projects, (2) there is a large number of toxic code snippets caused by a missing
license that are found in GitHub projects. %Moreover, the direction of copying
% is also unclear. The clones could come from Stack Overflow, the original
% project repositories, or other places.
\end{enumerate}

@@

We partially address this comment in the previous answer by performing an
empirical study of code cloning between toxic Stack Overflow code snippets and
GitHub projects. Furthermore, we also improved the paper on the aspect of the
awareness of information-seekers to toxic code snippets on Stack Overflow by
including the results from another survey of Stack Overflow visitors
(i.e.,~information seekers). This survey of the Stack Overflow visitors was
performed during the same time as the Stack Overflow answerers (25 July 2017 to
25 September 2017), and the full results are reported in our technical
report~\citep{Ragkhitwetsagul_RN2017}. We did not include the results in the
previous version of the paper due to a smaller sample size compared to the
answerers' survey. However, we did find some interesting results, so we have
included them in this version and discussed the key findings in~RQ1. The brief
summary of the visitor survey is as follows.

@@

The visitors' survey confirms the findings from the previous studies that Stack
Overflow code snippets can be problematic~\citep{Zhang2018,Acar2016,An2017}. Sixty-six
percent of the visitors experienced a problem from reusing Stack Overflow code
snippets ranging from incorrect solutions, outdated solutions, mismatched
solutions, to buggy code. Although they are aware of the problems, half of them
(56\%) never report back to the Stack Overflow discussions. On the other hand,
the visitors rarely give attributions to Stack Overflow when they reuse code
snippets from the website, similar to the findings reported
by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
license, and more than half of them never check for license compatibility when
reusing Stack Overflow code snippets. 
Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
check if the code snippet originated from a different source (e.g.,~an open source project) 
and if they had an incompatible license to their projects.
Moreover, we also found that 9\% of the participants
encountered legal issues by copying code from Stack Overflow. To the best of our
knowledge, a study of legal problems from reusing Stack Overflow code snippets
has never been done before and will be our future work.

@@

\begin{enumerate} \item We added a discussion of toxicity of outdated and
	license-incompatible clones on Stack Overflow. Although we found some harmful
	outdated clones, we could not find evidence that they are widely reused in open
	source projects on GitHub. Therefore, the damage is not high since there are only
	a few outdated code snippets that are harmful to reuse. On the other hand, the
	problem of license incompatibility caused by missing original licenses in Stack
	Overflow code snippets can cause more damage than outdated code. Different legal
	system and different interpretation of fair-use concept and de minimis (i.e.,~the
	minimal lines of code allowed to be copied without violating copyright) in each
	country can make reuse of these code snippets legally problematic.

@@

You are right. We mainly study online code clones and established their
existence. However, we used the term ``toxic code snippets'' to
emphasise the possible ramifications from online code cloning. Moreover, the
term code cloning is not well known outside the code cloning community. Code
clones are called differently in each research community or practice, such as
duplicated code, copy-and-paste code, code reuse, software similarity or
software redundancy. So, we decided not to use the term in the title.

@@

``Although this activity of online code cloning is well-known, there are only a
few empirical studies on the topic~\citep{An2017,Abdalkareem2017,Baltes2017},
especially on finding the origins of the clones. We tackle this challenge of
establishing the existence of online code clones and investigate how they occur in
this study.'' %Considering your suggestion and another suggestion by Reviewer 2
% that the definition of ``toxic code snippets'' is vague, we also tightened the
% definition of toxic code snippets to be more precise.

@@

That is a fair point, and we would like to analyse the statistics as you
suggested. To answer your question (a), the number of views is for the whole
Stack Overflow post but we use it as a proxy of the number of views the accepted
answer receives because the question and the answer of the two motivation
examples have a short gap of posting time (within the same day and four days
after). For (b), unfortunately, for our experiment we extracted only the code
snippets from the Stack Overflow dumps but not other information. They are the
only available data of the January 2016 snapshot we currently have. We checked
and found that the latest available Stack Overflow dump already contains
different data than the one we used in our study since it is more than 2
years newer, and will result in incorrect statistics and inconsistent results.
For (c), that is a really interesting idea. However, it is out of the scope of
this study and would involve extensive analysis of the data so we may
investigate it in the future work.

Nevertheless, we have added a footnote to the text in the Introduction to
clarify the point (a).

@@

Thank you for the detailed checking of the Stack Overflow post. Interestingly,
this is surprising to us as well. The comment in the post 22262310 by Joseph K
on 31 October 2017 that highlights the missing line in HADOOP \texttt{compare}
method is actually from a student in our class. His name is Joseph Kalash, and he
is a master student in Machine Learning MsC program at UCL Computer Science
department\footnote{Joseph's CV can be found here: \url{https://jkala.sh/cv}}.
We assigned a preprint of this paper to students in the COMPGS11 -- Research
Seminar in Software Engineering course and had a discussion about the paper on
Thu 2 November 2017. Joseph, who was an active Stack Overflow member, was one of
the students in the class and he actively participated in the discussion. It
seems that he had seen the Hadoop's toxic code snippet in the paper and decided
to post a comment to warn other users.

Nevertheless, since this is a very interesting suggestion, we also performed an
investigation of the 100 answers of our reported outdated code snippets on Stack
Overflow on 6 May 2018 to see if there is any comment to mitigate or point out
the toxicity of the code snippet. We include the result of this investigation in
RQ4. We found that out of 100 answers containing outdated code snippets,
6 answers had a comment saying the code in the answer is
outdated or contains issues (including Joseph's comment). Thus, there are about
6\% of outdated answers that were notified by the Stack Overflow users based on
our analysed data. None of the 6 answers change their outdated code, but the
comments themselves may help to warn other Stack Overflow users. We added this
discussion to RQ4.

@@

\begin{enumerate} 
	\item For the Stack Overflow data set, the value represents
	the median size of Stack Overflow code snippets. For the Qualitas data set, the
	value represents the median of the number of lines of code in each project. Since
	they are confusing as you pointed out, we decided to remove them from the table
	and only discuss the numbers in the text. 
	\item This is a great insight! We expanded the idea further and came up with a suggestion for an
	automated technique to facilitate human investigator on finding provenance and
	included it in a section called Automated cloning direction detection in the
	Overall Discussion. 
	\item Thanks. This has been fixed. \end{enumerate}

@@

\rcomment{ \textbf{The definition of toxic code snippets:} I understand that the
	authors are trying to put a new spin or name to the phenomena they study, but
	the definition the authors provide is, in my opinion, not sufficient. For
	example, their definition is ``toxic code snippets mean code snippets that are
	harmful to reuse and, \textbf{in several cases}, are caused by online...''. A
	definition should be clear - saying in several cases - means that in several
	other cases (1- your several cases) it is not harmful. So, I ask the authors to
	refine and clarify this definition, because as it stands now, this definition is
	confusing (at best). Given that your entire paper is about toxic code snippets,
	you can appreciate why this is important. }

We appreciate the comments. We have refined our definition of toxic code
snippets in the paper by adapting Israel Gat's definition~\citep{toxiccode}
which links toxic code to technical debt, i.e.~``a metaphor reflecting technical
compromises that can yield short-term benefit but may hurt the long-term health
of a software system''~\citep{Li2015}. The new definition of toxic doe snippets
is as follows.

``Toxic code snippets mean code snippets that, after incorporating into
software, the cost of paying back the technical debt exceeds the value it
generates in the long run.'' Stack Overflow code snippets cloned from open
source software or online sources can become toxic when they are (1)~outdated,
(2)~violating their original software license, (3) exhibiting code smells, or
(4) having security vulnerabilities. We chose to study toxic code snippets
caused by outdated code and license-violating code snippets in this study since
these two problems are still underexplored compared to code
smells~\citep{Tufano2015} or vulnerabilities~\citep{Acar2016,Fischer2017}.
Outdated code snippets can be harmful since they are not up-to-date with their
originals and may contain defects. Code snippets from open source projects
usually fall under a specific software license, e.g.,\ GNU General Public License
(GPL). If they are cloned to Stack Overflow answers without the license, and
then flow to other projects with conflicting licenses, legal issues may occur.

@@

Regarding RQ5 (the Stack Overflow answerer survey), that is a good point. Since
RQ5 supports the motivation of our experiment by showing that code
copying from software projects to Stack Overflow occurs and showing
that some of the answerers are not aware of outdated code and software license
incompatibility. We moved them to RQ1 instead and reorganised the paper to
discuss the survey results as an incentive for our experiment of online code
clone detection and toxic code snippet identification. The findings in RQ2--5
will confirm the survey results by showing that the issues actually occur on
Stack Overflow.

@@

Stack Overflow allows its users to edit their own posts,
i.e.,~questions/answers\footnote{https://meta.stackoverflow.com/questions/315915/i-am-not-allowed-to-edit-my-own-question}, or other user's posts\footnote{https://stackoverflow.com/help/privileges/edit}. Thus, if the code snippet in an answer is outdated and has an issue, the answerer or other high-reputation users can update the answer to be up-to-date or to warn other users that the code is already outdated and may contain problems. We found some discussions regarding this concern on Metaexchange as well so the Stack Overflow community is also considering this option\footnote{Discussion about outdated answer: https://meta.stackexchange.com/questions/131495/how-to-handle-outdated-answers and https://meta.stackexchange.com/questions/180864/editing-outdated-source-code-in-an-answer}. We included this discussion in the paper.

Based on your suggestion of looking at other newer or higher-voted answers, we
performed an investigation of all the answers in 100 posts containing outdated
code snippets as accepted answers. We found that there were 34 posts which
contain newer answers. Regarding the number of votes, there were 5 posts which
contained other answers with a higher number of votes than the outdated answer.
Ninety-nine out of the one hundred outdated code snippets were still marked as accepted
answers. This discussion of the findings is added to RQ4.

@@

Good point. Although we grouped the code modifications that make Stack Overflow
snippets outdated into 6 categories as shown in Table 9, we did not investigate
the motivation of the changes such as code refactoring or variable renaming. We
have performed the check as you suggested by checking the commit message of each
change that makes the code outdated. The findings are discussed below and are
included in RQ4.

We looked through the commit history of 100 outdated code snippets and
summarised the reasons for code updates. We carefully read the commit messages
and/or used the bug IDs in the commit messages to obtain more information from
the bug report systems. We summarised the reasons for code changes into 6 groups
as shown in the table below.

\begin{table}[H]
	\centering
	\begin{tabular}{llr}
		\toprule
		Intent & Detail & Amount \\
		\midrule
		Enhancement & Add or update existing features & 64 \\
		Deprecation & Delete dead/deprecated code & 15 \\
		Bug & Fix bugs & 10 \\
		Refactoring & Refactor code for better design & 6 \\
		Coding style & Update to a new style guideline & 3 \\
		Data change & Changes in the data format & 2 \\
		\bottomrule
	\end{tabular}
	\label{tab:intent_outdated}
	\caption{Intents of code changes in 100 outdated code snippets}
\end{table}

The majority (64) of the changes are due to code enhancement, such as adding
new features or improving existing code to support a newer version of the
language or APIs. Fifteen changes are for removal of dead or deprecated code
such as the SQL connection code example in Hibernate. Ten changes are made to
fix bugs in the software (e.g.,~array reference, race condition, wrong field
access, \texttt{NullPointerException}). There are 6 changes for code
refactoring, 3 changes for updating coding styles using an automated tool or
manually, and 2 changes that are caused by the change of data format.

@@

That is a fair point. The reason we chose the clone size of at least 10 lines is
because it is considered a standard setting for clone detection in large-scale
data sets to avoid trivial clones (e.g., \texttt{equals}, \texttt{hashCode}, or
getter and setter methods) in the analysis or the manual investigation
phase~\citep{Sajnani2016}.

@@

To measure the impact of this minimum clone size threshold on the clone results,
we performed an investigation of three different threshold values: six, ten, and
fifteen lines. We started our investigation by using a threshold value of six
lines, a well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
clone candidate pairs. We randomly sampled 382 pairs from the two sets for
a manual check. This sample number was a statistically significant sample with a
95\% confidence level and $\pm 5\%$ confidence interval. The first author
investigated the sampled clone pairs and classified them into three groups:
non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
setter methods), and non-trivial clones. The manual check found 26 non-clone
pairs; 322 trivial clone pairs, and 34 non-trivial clone pairs. Next, we
increased the threshold to ten lines, another well-established minimum clone
size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs
from Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and
manually checked the same amount of 382 pairs and found 27 non-clone pairs, 253
trivial clone pairs, and 102 non-trivial clone pairs. Then, we increased the
threshold further to fifteen lines and retrieved 196 clone pairs from Simian and
1,230 clone pairs from SourcererCC. The manual check of the 382 randomly sampled
pairs revealed zero non-clone pairs, 298 trivial clone pairs, and 83 non-trivial
clone pairs.

@@

We are grateful for the insightful comment. We selected the 2013 snapshot of
Qualitas data since it is the latest and the most complete snapshot (i.e.,~having
the highest number of Java projects) provided by the data set author.
